---
title: "Preprocess data for clustering"
author: "Orla"
date: "June 16, 2017"
output: html_document
---
#Libraries

Set up libraries needed. 

```{r lib_load, message = FALSE}
library(tidyverse)
library(caTools)
```


#Paths and files.

Set up the paths and filenames of the positive and negative cohorts. **Note the negative cohort is not yet available.** Here we assume that positive cohort which are read in have not been selected using the finalised set of inclusion and exclusion criteria.

```{r}
path <- "C:/Users/ODoyle/Documents/dev/feature_selection/"
setwd(path)
source("02_code/fs_funtions.R")

pos_data_file <- stringr::str_c(path, "/01_data/Positive_Cohort_v1_20170425.csv")
#neg_data_file <- stringr::str_c(path, "/01_data/<neg cohort file name..csv")

var_config_file <- stringr::str_c(path, "/01_data/sb_ppp_var_config.csv")
```

#Read data
Downsample the data so that it's the same size as the Strongbridge data set. 

```{r}
df <- read_rds(paste0("F:/Projects/Gilead/data/modelling/", "train_all_no_cm_date_diff_vars.rds"))
isb <- sample.split(df$label, SplitRatio = 0.211)
df_sb_size <- df[isb,] 
```

#Training and test splits
Partition the data sets into training and test splits. 

```{r}
itr <- sample.split(df_sb_size$label, SplitRatio = 0.75)
x_clustering_tr <- df_sb_size[itr,]
x_clustering_ts <- df_sb_size[!itr,]
```
#Write out the clustering data sets. 
```{r}
write.csv(x_clustering_tr, paste0(path, "/01_data/cluster_dfs/gilead/", "df_tr_clust.csv"))
write.csv(x_clustering_ts, paste0(path, "/01_data/cluster_dfs/gilead/", "df_ts_clust.csv"))

```


