---
title: "Raw LASSO"
author: "Orla"
date: "July 6, 2017"
output: html_document
---
#Libraries

Set up libraries needed. 

```{r lib_load, message = FALSE}
library(tidyverse)
library(glmnet)
```



```{r}
path <- "C:/Users/ODoyle/Documents/dev/feature_selection/"
setwd(path)
source("02_code/fs_funtions.R")

```


#Read data 
Read the training and test data. 
```{r}
df_tr <- read.csv(paste0(path, "/01_data/cluster_dfs/gilead/", "df_tr_clust.csv"), stringsAsFactors = FALSE)
df_ts <- read.csv(paste0(path, "/01_data/cluster_dfs/gilead/", "df_ts_clust.csv"), stringsAsFactors = FALSE)


```
Crude correction for missing values. 

```{r}
df_tr[is.na(df_tr)] <- 0 
df_ts[is.na(df_ts)] <- 0 
```


Extract the appropriate variables which in this case are the frequency variables. 

```{r}
df_tr %>% dplyr::select(label, contains("ave_claims_count")) -> vdf_tr
df_ts %>% dplyr::select(label, contains("ave_claims_count")) -> vdf_ts

```

#Modelling
Apply a gradient boosting trees model to the training dataset. 
```{r}
tr_data <-  as.matrix(as.data.frame(lapply(dplyr::select(vdf_tr, -label), as.numeric)))
xgb.fit <- xgboost(data = tr_data, label = vdf_tr$label,
max_depth = 6, eta = 0.3, nthread = 2, nrounds = 50,
objective = "binary:logistic")

```
Apply the trained model to the test dataset and extract the variable importance. 
```{r}
ts_data <-  as.matrix(as.data.frame(lapply(dplyr::select(vdf_ts, -label), as.numeric)))
xgb.pred <- predict(xgb.fit, ts_data)
write_rds(xgb.pred ,paste0(path,"/01_data/cluster_dfs/gilead/fit_xgb_raw.rds"))
```

Compute the importance table for the trained xgboost model. 
```{r}
importance_matrix <- xgb.importance(colnames(ts_data), model = xgb.fit)
write.csv(importance_matrix ,paste0(path,"/01_data/cluster_dfs/gilead/xgb_vi.csv"))
```

#Performance
To assess the performance of the model a precision-recall curve is used. 

```{r}
pr_xgb <- get_curve(xgb.pred, vdf_ts$label, "rec", "prec")
pr_xgb_bin <- bin_curve(pr_xgb, 20, agg_func=mean)
plot(pr_xgb_bin$x_binned, pr_xgb_bin$y)
write.csv(pr_xgb_bin ,paste0(path,"/01_data/cluster_dfs/gilead/pr_xgb_raw.csv"))
```



