---
title: "LASSO applied to aggregated variables"
author: "Orla"
date: "July 5, 2017"
output: html_document
---
#Libraries

Set up libraries needed. 

```{r lib_load, message = FALSE}
library(tidyverse)
library(xgboost)
```



```{r}
path <- "C:/Users/ODoyle/Documents/dev/feature_selection/"
setwd(path)
source("02_code/fs_funtions.R")

```

#Read data 
Read the training set which has already been aggregated.   
```{r}
adf_tr <- read_rds(paste0(path, "/01_data/cluster_dfs/gilead/", "x_clustering_tr_agg_mean.rds"))
colnames(adf_tr)[1] <- "label"
adf_tr[is.na(adf_tr)]=0
```

Read in the test data and cluster membership and use this to create aggregated variables for the test set. 

```{r}
df_ts <- read.csv(paste0(path, "/01_data/cluster_dfs/gilead/", "df_ts_clust.csv"), stringsAsFactors = FALSE)
df_ts %>% dplyr::select(contains("ave_claims_count")) -> df_ts_nolabel
hc <- read_rds(paste0(path, "/01_data/cluster_dfs/gilead/", "hc_cut.rds"))
tdf_ts <- as.data.frame(t(df_ts_nolabel))
ctdf_ts <- cbind(tdf_ts, hc)

ctdf_ts %>% 
  group_by(hc) %>% 
  summarise_each(funs(mean)) %>% 
  dplyr::select(-hc) -> actdf_ts

adf_ts <- cbind(df_ts$label, as.data.frame(t(actdf_ts)))
colnames(adf_ts)[1] <- "label"
adf_tr[is.na(adf_tr)]=0
```

#Modelling
Apply a logistic regression model with LASSO penalty to the aggreated variables in the training dataset. 
```{r}
tr_data <-  as.matrix(as.data.frame(lapply(dplyr::select(adf_tr, -label), as.numeric)))
xgb.fit <- xgboost(data = tr_data, label = adf_tr$label,
max_depth = 6, eta = 0.3, nthread = 2, nrounds = 50,
objective = "binary:logistic")

```
Apply the trained model to the test dataset and extract the variable importance. 
```{r}
ts_data <-  as.matrix(as.data.frame(lapply(dplyr::select(adf_ts, -label), as.numeric)))
xgb.pred <- predict(xgb.fit, ts_data)
write_rds(xgb.fit ,paste0(path,"/01_data/cluster_dfs/gilead/fit_xgb_cluster_mean.rds"))
```

Compute the importance table for the trained xgboost model.
```{r}
importance_matrix <- xgb.importance(colnames(ts_data), model = xgb.fit)
write.csv(importance_matrix ,paste0(path,"/01_data/cluster_dfs/gilead/vi_xgb_cluster_mean.csv"))
```
#Performance
To assess the performance of the model a precision-recall curve is used. 

```{r}
pr_xgb <- get_curve(xgb.pred, adf_ts$label, "rec", "prec")
pr_xgb_bin <- bin_curve(pr_xgb, 20, agg_func=mean)
plot(pr_xgb_bin$x_binned, pr_xgb_bin$y)
write.csv(pr_xgb_bin ,paste0(path,"/01_data/cluster_dfs/gilead/pr_xgb_cluster_mean.csv"))
```
