---
title: "Group LASSO"
author: "Orla"
date: "June 20, 2017"
output: html_document
---
#Libraries

Set up libraries needed. 

```{r lib_load, message = FALSE}
library(tidyverse)
library(grpreg)
library(gglasso)
library(palabmod)
```



```{r}
data_dir <- "F:/Projects/Strongbridge/data/feature_selection/"
# setwd(path)
 source("C:/Users/ODoyle/Documents/dev/feature_selection/02_code/fs_funtions.R")
results_dir <- "F:/Projects/Strongbridge/results/feature_selection/Clustering/Lasso_top_coded/"

```


#Read data 
Read the training and test data. 
```{r}
df_tr <- read_rds(paste0(data_dir, "train_clustering_rm_3592_capped_p99.rds"))
df_ts <- read_rds(paste0(data_dir, "test_clustering_rm_3592_capped_p99.rds"))


```
Crude correction for missing values. 

```{r}
# Missing vals already imputed
# df_tr[is.na(df_tr)] <- 0 
# df_ts[is.na(df_ts)] <- 0
```


Extract the appropriate variables which in this case are the frequency variables. 

```{r}
df_tr %>% dplyr::select(label, dplyr::contains("CLAIM")) -> vdf_tr
df_ts %>% dplyr::select(label, dplyr::contains("CLAIM")) -> vdf_ts

# set D_3592 to 0

```

Read in the cluster memberships. These will serve as the groupings for group LASSO. 

```{r}
hc <- read_rds(paste0(results_dir, "hc_cut_400.rds"))
```


#Group LASSO model


Train the group LASSO model providing the cluster memberships as the groups. The data frame is converted to a numeric matrix before processing. Implementations are provided for both the gglasso (https://cran.r-project.org/web/packages/gglasso/gglasso.pdf) and grpreg package (https://cran.r-project.org/web/packages/grpreg/grpreg.pdf). Initial tests suggested that the grpreg package is faster however the gglasso package is the more popular of the two. 

```{r}
#tr_data <- data.matrix(dplyr::select(vdf_tr, -label))
tr_data <-  as.matrix(as.data.frame(lapply(dplyr::select(vdf_tr, -label), as.numeric)))
grpl.fit <- grpreg(tr_data, vdf_tr$label, hc, penalty = "grLasso",family="binomial")
write_rds(grpl.fit,paste0(results_dir,"fit_glasso_cluster.rds"))

grpl.fit <- read_rds(paste0(results_dir,"fit_glasso_cluster.rds"))
# find which lambda corresponds to approx 300 predictors:
vars_per_lambda <- apply(grpl.fit$beta, 2, function(x) { length(x[abs(x) > 0])})

#tr_label <-vdf_tr$label
#tr_label[tr_label == 0]<- -1
#grpl.fit <- gglasso(tr_data,tr_label,group=hc,loss="logit")
```

Extract the coefficients of the model at the cross-validated fit for lambda or alternatively at a user specified value for lambda. 
Note that the CV does not take into account the imbalance in the data so may not be the optimal choice. 

```{r}
# lambda_user <- 0.00001
lambda_user <- 0.0014
#lasso.cvfit.coef <- as.data.frame(as.matrix(coef(grpl.fit, s = "lambda.min")))
#write_csv(lasso.cvfit.coef,paste0(results_dir,"vi_glasso_cluster.csv"))
```

Once the model has been fitted, the weights of the coefficients can plotted against lambda. 
```{r}
plot(grpl.fit)

```

```{r}
# grpl.cvfit <- cv.grpreg(tr_data, vdf_tr$label, hc, penalty = "grLasso",family="binomial", nfolds = 5)
#plot(grpl.cvfit)
#grpl.cvfit <- cv.gglasso(tr_data, tr_label, group=hc, loss = "logit", pred.loss = "loss", nfolds = 5)
```


Use the trained model to provide predictions on the test set. This requires that lambda is either set to some default value or optimised using CV. 

```{r}
#ts_data<- data.matrix(dplyr::select(vdf_ts, -label))
#ts_data <-  as.matrix(as.data.frame(lapply(dplyr::select(vdf_ts, -label), as.numeric)))
ts_data <-  as.matrix(dplyr::select(vdf_ts, -label))
# grpl.pred <- predict(grpl.fit, ts_data, type="response", s = lambda_user)
# I altered the code to the following:
grpl.pred.all <- predict(grpl.fit, ts_data, type="response", s = lambda_user)
grpl.pred <- grpreg:::predict.grpreg(grpl.fit, ts_data, type="response", lambda = lambda_user)

#grpl.pred <- predict(grpl.fit,type="link",newx=ts_data, s=0.0001)
#grpl.prob <- exp(grpl.pred_ts)/(1+exp(grpl.pred_ts))
``` 

#Performance
To assess the performance of the model a precision-recall curve is used. 

```{r}
pr_grpl <- get_curve(grpl.pred, vdf_ts$label, "rec", "prec")
pr_grpl_bin <- bin_curve(pr_grpl, 20, agg_func=mean)
plot(pr_grpl_bin$x_binned, pr_grpl_bin$y)
write.csv(pr_grpl_bin,paste0(results_dir,"lam_0.00014_pr_glasso_cluster.csv"))
```



